Designing for Complex Gig Work and Careers

### 2017-03-07 proposals/SIGFproposal_2017/ali_alkhatib_sigf.tex
cleared out the bulleted list of suggestions

% Michael Bernstein [5:42 PM] 
% feedback:
% [x] first paragraph: "gig work” needs examples (Uber, Mechanical Turk) so people know what you’re talking about. I know you get there in the second paragraph, but I think a reader will tune out the first paragraph if they don’t know concretely what you’re talking about.
% [x] research plan: I’d like to see a stronger transition. Ideally, a question that the historical analysis left open that you are now poised to answer
% [x] research plan: make clearer that your proposal is to transition this historical framing into a novel system that you are building (I don’t think that readers will automatically know this)
% [ ] research plan: whoa, you jump to experimental analysis before you even describe what it is! I need 1-2 paragraphs describing the system that you’re building. Walk through what it does, what a worker will do with it.
% [x] research plan: can cut the third paragraph for space if needed
% [ ] interdisciplinarity: call out the obvious: that you are a trained social scientist now in a computer science department

@@

\begin{blah}
% [ ] research plan: whoa, you jump to experimental analysis before you even describe what it is! I need 1-2 paragraphs describing the system that you’re building. Walk through what it does, what a worker will do with it.
% \topic{1--2 paragraphs describing the system. What does it do? what will workers do with it?}
\topic{The system we intend to build will serve two roles --- one for workers and one for employers.} % that the worker can curate and that requesters and platforms at large can access to make hiring decisions algorithmically.
Gig workers will share their work histories from platforms such as Amazon Mechanical Turk with our repository,
which will allow us to provide the worker with information upon which they can reflect
(e.g. detailed analysis of their work trends, approval rates under various circumstances, etc\dots)
as well as information in relation to other workers
(e.g. offering a percentile ranking overall for approval rates, or within specific types of tasks).
In doing so, we hope to find that workers will identify cues and gravitate toward qualities in work
in which they identify competitive advantage (for example, )

\topic{The second aspect }
and second, we will incorporate their data into responses from platforms and employers looking for workers qualified to do complex work.

By disconnecting workers' data from the platforms themselves, our repository will act as a sort of ``digital hiring hall'',
connecting employers with workers whose varied work histories provide them with the expertise necessary to do given tasks.
\end{blah}

@@

\section*{Interdisciplinarity}
\topic{This research will call on methods and skills originally from and generally found in disparate fields.}
As we showed with our paper examining the relationship between piecework and gig work~\cite{pieceworkCrowdworkGigwork},
the lens of a social scientist can inform conversations about digitally mediated work in ways that many computer scientists are not otherwise able to offer.
At the same time, the perspectives of computer scientists
--- and the challenges digitally mediated spaces bring with them ---
offer to reinvigorate deeply theoretically grounded discussion and offer field sites with which to experiment and test these theories.

>>>>

% Michael Bernstein [5:42 PM] 
% feedback:
% [x] first paragraph: "gig work” needs examples (Uber, Mechanical Turk) so people know what you’re talking about. I know you get there in the second paragraph, but I think a reader will tune out the first paragraph if they don’t know concretely what you’re talking about.
% [x] research plan: I’d like to see a stronger transition. Ideally, a question that the historical analysis left open that you are now poised to answer
% [x] research plan: make clearer that your proposal is to transition this historical framing into a novel system that you are building (I don’t think that readers will automatically know this)
% [x] research plan: whoa, you jump to experimental analysis before you even describe what it is! I need 1-2 paragraphs describing the system that you’re building. Walk through what it does, what a worker will do with it.
% [x] research plan: can cut the third paragraph for space if needed
% [x] interdisciplinarity: call out the obvious: that you are a trained social scientist now in a computer science department

@@

% \begin{blah}
% [ ] research plan: whoa, you jump to experimental analysis before you even describe what it is! I need 1-2 paragraphs describing the system that you’re building. Walk through what it does, what a worker will do with it.
% \topic{1--2 paragraphs describing the system. What does it do? what will workers do with it?}
\topic{The system we intend to build will serve two roles --- one for workers and one for employers.} % that the worker can curate and that requesters and platforms at large can access to make hiring decisions algorithmically.
Gig workers will share their work histories from platforms such as Amazon Mechanical Turk with our repository,
which will allow us to provide the worker with information upon which they can reflect
(e.g. detailed analysis of their work trends, approval rates under various circumstances, etc\dots)
as well as information in relation to other workers
(e.g. offering a percentile ranking overall for approval rates, or within specific types of tasks).
In doing so, we hope to find that workers will identify cues and gravitate toward qualities in work
in which they identify competitive advantage.

\topic{The second role that this repository will help employers identify and source the best workers for highly skilled work.}
By aggregating the data from work platforms and
offering more in--depth analysis of workers' histories, we hope to find that
we can direct employers to gig workers whose overall experiences match the employer's given needs.
For example, if an employer or a platform queries our platform for
workers who are proficient at translating between two specific languages,
we can yield a list of workers who would be suitable for the task.

\topic{This approach is similar in some senses to the role that hiring halls played through the \nth{20} century.}
By disconnecting workers' data from the platforms themselves, our repository will act as a sort of ``digital hiring hall'',
connecting employers with workers whose varied work histories provide them with the expertise necessary to do given tasks.
By engaging workers in the management of this repository, we will advance the metaphor in much the same way that
labor unions maintained --- and continue to operate --- hiring halls of their workers.

% \end{blah}

@@

\section*{Interdisciplinarity}
\topic{This research will call on methods and skills originally from and generally found in disparate fields.}
As we showed with our paper examining the relationship between piecework and gig work~\cite{pieceworkCrowdworkGigwork},
the lens of a social scientist can inform conversations about digitally mediated work in ways that many computer scientists are not otherwise able to offer.
At the same time, the perspectives of computer scientists
--- and the challenges digitally mediated spaces bring with them ---
offer to reinvigorate deeply theoretically grounded discussion and offer field sites with which to experiment and test these theories.
As a Computer Science Ph.D. student originally trained as an Anthropologist, I believe
I'm the best candidate to combine these bodies of literature to make this project succeed.
